Inpainting with dimensionality reduction in the Fourier domain

### 2011-06-20 project/Paper/paper.tex
Paper: File extensions.
+ Work on paper

%\usepackage{times}
%\usepackage{balance}
\usepackage{url}
\usepackage{graphicx}
\usepackage[pdftex]{hyperref}
\usepackage[utf8]{inputenc}

@@

Because we thought it not feasable to tune all the parameters by hand, we wrote a program to
do the offline parameter estimation. The idea is to do this once for a few representative images, and get
parameters that can model as closely as possible many of the images we are interested in.
Our proposed method combines a gradient descent method with ideas from cross-validation, and tunes our
10-dimensional parameter-space, maximising time and accuracy.

\subsubsection{Error function}

@@

\begin{table*}[htbp]
  \centering
  \begin{tabular}[c]{|l||l|l|l|}
    \hline
    Basis&Support&Suitable signals&Unsuitable signals\\
    \hline
    Fourier&global&sine like&localized\\
    wavelet&local&localized&sine like\\
    \hline
  \end{tabular}
  \caption{Characteristics of Fourier and wavelet basis.}
  \label{tab:fourier-wavelet}
\end{table*}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/boundaryArtifact_noframe}
  \caption{Artifacts that occur without a frame (frame size = 0). The patches are recognizable in the reconstruction}
  \label{fig:boundaryArtifacts}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/imageFraming}
  \caption{Only the inner patch (marked red) is reconstructed in one step while the frame only provides additional signal. (Undistorted image shown) }
  \label{fig:framing}
\end{figure}

>>>>

%\usepackage{times}
%\usepackage{balance}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage[pdftex]{hyperref}
\usepackage[utf8]{inputenc}

@@

Because we thought it not feasable to tune all the parameters by hand, we wrote an algorithm to
do the offline parameter estimation. The idea is to do this once for a few representative images, and get
parameters that can model as closely as possible many of the images we are interested in.
Our proposed method combines a gradient descent method with ideas from cross-validation, and tunes our
10-dimensional parameter-space, maximising time and accuracy.

\subsubsection{Error function}
When doing a minimization of any kind, an error function is needed. Of course we already had the error function
of the evaluation script, that gives a mean over the squared differences of the reconstructed to the original
image. However, using only an error measure, the time would potentially grow to infinity to get the best accuracy possible during tuning.

Therefore we tried different error function including both, the image error $E$, and the time $T$ spent. The image error here is the average
squared error of a reconstructed pixel to the original pixel, scaled with a factor (usually about 10000), while the time is measured in seconds.

\begin{table*}
  \centering
  \begin{tabular}{|l|p{5cm}|p{5cm}|}
    \hline
    Function&Advantages&Disadvantages\\
    \hline
    $\exp(E)+\exp(T)$ & Increases cost fast to avoid $E$ or $T$ over a certain threshold & Not enough gradient for very low $E$, $T$ values\\
    \hline
    $(1-\exp(E))*(1-\exp(T))$ & Makes it possible to have large times for very low errors & Works also the other way around, and optimization only minimizes time\\
    \hline
    $E + T$ & Everywhere a good gradient & Time from 60 to 59 seconds is same \textit{improvement} as time from 2 to 1 second\\
    \hline
    $\begin{cases}
  \exp(E)  & \text{if }T<60\\
  \exp(E)+\exp(T/60 - 1) - 1 & \text{else}
\end{cases}$ & Optimizes for error only when time is low enough. Function still continous, penalizes high times. & None so far, this is the function used by us\\
    \hline
  \end{tabular}
  \caption{Different combined error functions}
  \label{error_function_table}
\end{table*}

@@

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/boundaryArtifact_noframe.png}
  \caption{Artifacts that occur without a frame (frame size = 0). The patches are recognizable in the reconstruction}
  \label{fig:boundaryArtifacts}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\columnwidth]{images/imageFraming.png}
  \caption{Only the inner patch (marked red) is reconstructed in one step while the frame only provides additional signal. (Undistorted image shown) }
  \label{fig:framing}
\end{figure}
